---
title: "First Year Exam Question 10"
author: "Julia Napoli"
date: "7/9/2022"
output:
  pdf_document: default
  html_document: default
---

PID: A59010574

## Question 10

First, we must download the most updated covid-19 data from the website provided by Barry.

Now, let's read it into the workspace.

```{r}
covid_data <- read.csv("covid-19-variant-data.csv")
```

And now we can work on plotting the data. Let's get the ggplot, lubridate and dplyr libraries uploaded.

```{r}
library(ggplot2)
library(lubridate, warn.conflicts = FALSE)
library(dplyr)
```

Now we can think about plotting the data. First, let's erase the "total" and "other" rows that we don't need.
```{r}
# erase the "total" rows
no_total_covid_data <- covid_data %>% filter(!grepl('Total', variant_name))

# erase the "other" rows
new_covid_data <- no_total_covid_data %>% filter(!grepl('Other', variant_name))
```

Now let's convert the date data into date variables in R. 
```{r}
new_covid_data$date <- as.POSIXct(new_covid_data$date)
```



```{r}
covid_plot <- ggplot(data=new_covid_data, aes(x=date, y=percentage, group=variant_name, colour = variant_name)) +
  geom_line() + theme(legend.title=element_blank()) + scale_x_datetime(date_breaks = '1 month', date_labels = "%b-%Y") + theme(axis.text.x = element_text(angle = 60, hjust = 1))

print(covid_plot + ggtitle("Covid-19 Variants in California") + labs(y = "Percentage of sequenced specimens"))
```

All done!
